---
params:
  subtitle: ""
  title: ""
  authors: ""
title: '`r params$title`'
subtitle: '`r params$subtitle`'
author: '`r params$authors`'
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: TRUE
  bookdown::pdf_document2:
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
    fig_width: 5
always_allow_html: yes
bibliography: '`r here::here("bibliography.bib")`'
---

```{r knitrSetup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # by default turn off code echo
```

# A basic .Rmd template to illustrate our workflow

## Data

The following uses `skimr::skim()` to describe the data. Remember we created the skim output object in the R script. We just report it here.

```{r reportSkim}
# print out the skimr object by getting drake to bring it back from wherever
# it is hidden
drake::readd(skimTable) 
```

There's quite a lot of data...

## Plot

\@ref(fig:allDataPlot) plots every data point in the data (!). Remember we created the plot output object in the R script. We just print it here.

```{r allDataPlot, fig.cap="Half-hourly generation (GW)"}
# render the plot by getting drake to bring it back from wherever
# it is hidden
drake::readd(gWPlot)
```

# Runtime

```{r check runtime, include=FALSE}
t <- proc.time() - startTime
elapsed <- t[[3]]
```

Report generated in `r round(elapsed,2)` seconds ( `r round(elapsed/60,2)` minutes) using [knitr](https://cran.r-project.org/package=knitr) in [RStudio](http://www.rstudio.com) with `r R.version.string` running on `r R.version$platform`.

# R environment

## R packages used

 * base R [@baseR]
 * bookdown [@bookdown]
 * data.table [@data.table]
 * drake [@drake]
 * ggplot2 [@ggplot2]
 * here [@here]
 * knitr [@knitr]
 * lubridate [@lubridate]
 * rmarkdown [@rmarkdown,@rmarkdownBook]

## Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

# References

